Supplement to ``{\mytitle}''

### 2022-09-05 si/si.Rnw
Changed renamed functions

<<Model3Replication, echo=FALSE, cache=TRUE>>=
plot_order <- c(
  'Artibonite',
  'Sud_Est',
  'Nippes',
  'Nord_Est',
  'Ouest',
  'Centre',
  'Nord',
  'Sud',
  'Nord_Ouest',
  'Grande_Anse'
)

@@

lee3 <- haiti3()
lee3_sims <- simulate(lee3, nsim = 1000, seed = 321, format = 'data.frame')

>>>>

<<Model3Replication, echo=FALSE, cache=TRUE>>=
NSIM <- switch(run_level, 50, 100, 1000)

plot_order <- c(
  'Artibonite',
  'Sud_Est',
  'Nippes',
  'Nord_Est',
  'Ouest',
  'Centre',
  'Nord',
  'Sud',
  'Nord_Ouest',
  'Grande_Anse'
)

@@

lee3 <- haiti3_lee_et_al()
lee3_sims <- simulate(lee3, nsim = NSIM, seed = 321, format = 'data.frame')
